PANCHANGE_analysis

### 2020-09-03 PANCHANGE_analysis.Rmd
Reorganised the regression models and created prepan-baseline and retro-baseline models for all disorders.

Exclude GLAD/EDGI individuals that didn't take part in COPING
Exclude individuals with NA for the MHD categories

@@

# Create data set per cohort
++MD: Do we want to break up the datasets by cohort again? Or is this breaking up datasets into GAD

@@

# Create additional datasets for analyses
Filter data frame to create 3 datasets:

  1. Retrospective - baseline change anlyses
        i. Exclude individuals with NAs for:
              1. MHD
              2. Age
              3. Gender
              4. Missing retrospective and/or baseline data
  2. Prepandemic - baseline change analyses
          i. Exclude individuals with NAs for:
              1. MHD
              2. Age
              3. Gender
              4. Missing pandemic and/or baseline data
          ii. Exclude individuals with prepandemic data collected after 1st March.

@@

Model 0a: Disorder_hierarchical
```{r Model 0a: Disorder_hierarchical}
model0a <- lm(
  formula = gad.diff_score_base_prepan ~ Disorder_hierarchical,
  data = dat.gad)

summary(model0a)
```

Model 0b: Disorders
```{r}
model0b <- lm(
  formula = ocir.diff_score_base_prepan ~
    anxiety_disorders +
    depressive_disorders +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder,
  data = dat)

summary(model0b)
```

Model 0: Disorders
```{r}
model0 <- lm(
  formula = gad.diff_score_base_prepan ~ Disorder,
  data = dat)

summary(model0)
```

```{r}
tidy(model0)
```

Model 1: Model 0 + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r}
model1 <- lm(
  formula = phq.diff_score_base_prepan ~
    anxiety_disorders +
    depressive_disorders +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder +
    Gender_collapsed + age_category + Ethnicity_collapsed + time_diff_sign_up_coping,
  data = dat)

summary(model1)
```

Model 1: Model 0 + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r}
model1 <- lm(
  formula = pcl.diff_score_base_prepan ~ Disorder_hierarchical + Gender_collapsed + age_category + Ethnicity_collapsed + time_diff_sign_up_coping,
  data = dat)

summary(model1)
```

Model 1: Model 0 + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r}
model1 <- lm(
  formula = gad.diff_score_base_prepan ~ Disorder + Gender_collapsed + Age + Ethnicity_collapsed + time_diff_sign_up_coping,
  data = dat)

summary(model1)
```

>>>>

Exclude GLAD/EDGI individuals that didn't take part in COPING
Exclude individuals with NA for the MHD categories
Individuals with NAs for age/gender have already been excluded in pre-processing script.

@@

# Create data set per measure
++MD: Do we want to break up the datasets by measure? I think the datasets we've already specified should be sufficient. I've tested the results of the regression model and it's the same using dat.gad vs. dat datasets.

@@

# Create additional datasets for analyses
Filter data frame to create 2 additional datasets. Additional exclusion criteria (beyond those listed above) are specified below:

  1. Retrospective - baseline change anlyses
        i. Exclude individuals missing retrospective and/or baseline data
  2. Prepandemic - baseline change analyses
          i. Exclude individuals missing pandemic and/or baseline data
          ii. Exclude individuals with prepandemic data collected after 1st March.

@@

Model naming conventions:
0 - unadjusted
1 - adjusted
a - hierarchical disorders
b - overlapping disorder categories

++MD: We may want to exclude disorders from Model b that aren't including in the hierarchy (e.g. ADHD, ASD)

## Prepan-baseline change

### GAD
Model 0a: Disorder_hierarchical, Unadjusted
```{r GAD prepan Model 0a}
gad_prepan_model0a <- lm(
  formula = gad.diff_score_base_prepan ~ 
    Disorder_hierarchical,
  data = dat.prepan)

summary(gad_prepan_model0a)
tidy(gad_prepan_model0a)
```

Model 0b: Overlapping disorders, Unadjusted
```{r GAD prepan Model 0b}
gad_prepan_model0b <- lm(
  formula = gad.diff_score_base_prepan ~
    anxiety_disorders +
    depressive_disorders +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder,
  data = dat.prepan)

summary(gad_prepan_model0b)
tidy(gad_prepan_model0b)
```

Model 1a: Disorder hierarchical, Adjusted
  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r GAD prepan Model 1a}
gad_prepan_model1a <- lm(
  formula = gad.diff_score_base_prepan ~ 
    Disorder_hierarchical + 
    Gender_collapsed + 
    age_category + 
    Ethnicity_collapsed + 
    time_diff_sign_up_coping,
  data = dat.prepan)

summary(gad_prepan_model1a)
tidy(gad_prepan_model1a)
```

Model 1b: Overlapping disorders, Adjusted
  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r GAD prepan Model 1b}
gad_prepan_model1b <- lm(
  formula = gad.diff_score_base_prepan ~
    anxiety_disorders +
    depressive_disorders +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder +
    Gender_collapsed + age_category + Ethnicity_collapsed + time_diff_sign_up_coping,
  data = dat.prepan)

summary(gad_prepan_model1b)
tidy(gad_prepan_model1b)
```

### PHQ
Model 0a: Disorder_hierarchical, Unadjusted
```{r PHQ prepan Model 0a}
phq_prepan_model0a <- lm(
  formula = phq.diff_score_base_prepan ~ 
    Disorder_hierarchical,
  data = dat.prepan)

summary(phq_prepan_model0a)
tidy(phq_prepan_model0a)
```

Model 0b: Overlapping disorders, Unadjusted
```{r PHQ prepan Model 0b}
phq_prepan_model0b <- lm(
  formula = phq.diff_score_base_prepan ~
    anxiety_disorders +
    depressive_disorders +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder,
  data = dat.prepan)

summary(phq_prepan_model0b)
tidy(phq_prepan_model0b)
```

Model 1a: Disorder hierarchical, Adjusted
  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r PHQ prepan Model 1a}
phq_prepan_model1a <- lm(
  formula = phq.diff_score_base_prepan ~ 
    Disorder_hierarchical + 
    Gender_collapsed + 
    age_category + 
    Ethnicity_collapsed + 
    time_diff_sign_up_coping,
  data = dat.prepan)

summary(phq_prepan_model1a)
tidy(phq_prepan_model1a)
```

Model 1b: Overlapping disorders, Adjusted
  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r PHQ prepan Model 1b}
phq_prepan_model1b <- lm(
  formula = phq.diff_score_base_prepan ~
    anxiety_disorders +
    depressive_disorders +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder +
    Gender_collapsed + age_category + Ethnicity_collapsed + time_diff_sign_up_coping,
  data = dat.prepan)

summary(phq_prepan_model1b)
tidy(phq_prepan_model1b)
```

### PCL
Model 0a: Disorder_hierarchical, Unadjusted
```{r PCL prepan Model 0a}
pcl_prepan_model0a <- lm(
  formula = pcl.diff_score_base_prepan ~ 
    Disorder_hierarchical,
  data = dat.prepan)

summary(pcl_prepan_model0a)
tidy(pcl_prepan_model0a)
```

Model 0b: Overlapping disorders, Unadjusted
```{r PCL prepan Model 0b}
pcl_prepan_model0b <- lm(
  formula = pcl.diff_score_base_prepan ~
    anxiety_disorders +
    depressive_disorders +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder,
  data = dat.prepan)

summary(pcl_prepan_model0b)
tidy(pcl_prepan_model0b)
```

Model 1a: Disorder hierarchical, Adjusted
  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r PCL prepan Model 1a}
pcl_prepan_model1a <- lm(
  formula = pcl.diff_score_base_prepan ~ 
    Disorder_hierarchical + 
    Gender_collapsed + 
    age_category + 
    Ethnicity_collapsed + 
    time_diff_sign_up_coping,
  data = dat.prepan)

summary(pcl_prepan_model1a)
tidy(pcl_prepan_model1a)
```

Model 1b: Overlapping disorders, Adjusted
  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r PCL prepan Model 1b}
pcl_prepan_model1b <- lm(
  formula = pcl.diff_score_base_prepan ~
    anxiety_disorders +
    depressive_disorders +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder +
    Gender_collapsed + age_category + Ethnicity_collapsed + time_diff_sign_up_coping,
  data = dat.prepan)

summary(pcl_prepan_model1b)
tidy(pcl_prepan_model1b)
```

### OCIR
Model 0a: Disorder_hierarchical, Unadjusted
```{r OCIR prepan Model 0a}
ocir_prepan_model0a <- lm(
  formula = ocir.diff_score_base_prepan ~ 
    Disorder_hierarchical,
  data = dat.prepan)

summary(ocir_prepan_model0a)
tidy(ocir_prepan_model0a)
```

Model 0b: Overlapping disorders, Unadjusted
```{r OCIR prepan Model 0b}
ocir_prepan_model0b <- lm(
  formula = ocir.diff_score_base_prepan ~
    anxiety_disorders +
    depressive_disorders +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder,
  data = dat.prepan)

summary(ocir_prepan_model0b)
tidy(ocir_prepan_model0b)
```

Model 1a: Disorder hierarchical, Adjusted
  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r OCIR prepan Model 1a}
ocir_prepan_model1a <- lm(
  formula = ocir.diff_score_base_prepan ~ 
    Disorder_hierarchical + 
    Gender_collapsed + 
    age_category + 
    Ethnicity_collapsed + 
    time_diff_sign_up_coping,
  data = dat.prepan)

summary(ocir_prepan_model1a)
tidy(ocir_prepan_model1a)
```

Model 1b: Overlapping disorders, Adjusted
  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r OCIR prepan Model 1b}
ocir_prepan_model1b <- lm(
  formula = ocir.diff_score_base_prepan ~
    anxiety_disorders +
    depressive_disorders +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder +
    Gender_collapsed + age_category + Ethnicity_collapsed + time_diff_sign_up_coping,
  data = dat.prepan)

summary(ocir_prepan_model1b)
tidy(ocir_prepan_model1b)
```

## Retro-baseline change

### GAD
Model 0a: Disorder_hierarchical, Unadjusted
```{r GAD retro Model 0a}
gad_retro_model0a <- lm(
  formula = gad.diff_score_base_retro ~ 
    Disorder_hierarchical,
  data = dat.retro)

summary(gad_retro_model0a)
tidy(gad_retro_model0a)
```

Model 0b: Overlapping disorders, Unadjusted
```{r GAD retro Model 0b}
gad_retro_model0b <- lm(
  formula = gad.diff_score_base_retro ~
    anxiety_disorders +
    depressive_disorders +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder,
  data = dat.retro)

summary(gad_retro_model0b)
tidy(gad_retro_model0b)
```

Model 1a: Disorder hierarchical, Adjusted
  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r GAD retro Model 1a}
gad_retro_model1a <- lm(
  formula = gad.diff_score_base_retro ~ 
    Disorder_hierarchical + 
    Gender_collapsed + 
    age_category + 
    Ethnicity_collapsed + 
    time_diff_sign_up_coping,
  data = dat.retro)

summary(gad_retro_model1a)
tidy(gad_retro_model1a)
```

Model 1b: Overlapping disorders, Adjusted
  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r GAD retro Model 1b}
gad_retro_model1b <- lm(
  formula = gad.diff_score_base_retro ~
    anxiety_disorders +
    depressive_disorders +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder +
    Gender_collapsed + age_category + Ethnicity_collapsed + time_diff_sign_up_coping,
  data = dat.retro)

summary(gad_retro_model1b)
tidy(gad_retro_model1b)
```

### PHQ
Model 0a: Disorder_hierarchical, Unadjusted
```{r PHQ retro Model 0a}
phq_retro_model0a <- lm(
  formula = phq.diff_score_base_retro ~ 
    Disorder_hierarchical,
  data = dat.retro)

summary(phq_retro_model0a)
tidy(phq_retro_model0a)
```

Model 0b: Overlapping disorders, Unadjusted
```{r PHQ retro Model 0b}
phq_retro_model0b <- lm(
  formula = phq.diff_score_base_retro ~
    anxiety_disorders +
    depressive_disorders +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder,
  data = dat.retro)

summary(phq_retro_model0b)
tidy(phq_retro_model0b)
```

Model 1a: Disorder hierarchical, Adjusted
  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r PHQ retro Model 1a}
phq_retro_model1a <- lm(
  formula = phq.diff_score_base_retro ~ 
    Disorder_hierarchical + 
    Gender_collapsed + 
    age_category + 
    Ethnicity_collapsed + 
    time_diff_sign_up_coping,
  data = dat.retro)

summary(phq_retro_model1a)
tidy(phq_retro_model1a)
```

Model 1b: Overlapping disorders, Adjusted
  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r PHQ retro Model 1b}
phq_retro_model1b <- lm(
  formula = phq.diff_score_base_retro ~
    anxiety_disorders +
    depressive_disorders +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder +
    Gender_collapsed + age_category + Ethnicity_collapsed + time_diff_sign_up_coping,
  data = dat.retro)

summary(phq_retro_model1b)
tidy(phq_retro_model1b)
```

### PCL
Model 0a: Disorder_hierarchical, Unadjusted
```{r PCL retro Model 0a}
pcl_retro_model0a <- lm(
  formula = pcl.diff_score_base_retro ~ 
    Disorder_hierarchical,
  data = dat.retro)

summary(pcl_retro_model0a)
tidy(pcl_retro_model0a)
```

Model 0b: Overlapping disorders, Unadjusted
```{r PCL retro Model 0b}
pcl_retro_model0b <- lm(
  formula = pcl.diff_score_base_retro ~
    anxiety_disorders +
    depressive_disorders +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder,
  data = dat.retro)

summary(pcl_retro_model0b)
tidy(pcl_retro_model0b)
```

Model 1a: Disorder hierarchical, Adjusted
  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r PCL retro Model 1a}
pcl_retro_model1a <- lm(
  formula = pcl.diff_score_base_retro ~ 
    Disorder_hierarchical + 
    Gender_collapsed + 
    age_category + 
    Ethnicity_collapsed + 
    time_diff_sign_up_coping,
  data = dat.retro)

summary(pcl_retro_model1a)
tidy(pcl_retro_model1a)
```

Model 1b: Overlapping disorders, Adjusted
  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r PCL retro Model 1b}
pcl_retro_model1b <- lm(
  formula = pcl.diff_score_base_retro ~
    anxiety_disorders +
    depressive_disorders +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder +
    Gender_collapsed + age_category + Ethnicity_collapsed + time_diff_sign_up_coping,
  data = dat.retro)

summary(pcl_retro_model1b)
tidy(pcl_retro_model1b)
```

### OCIR
Model 0a: Disorder_hierarchical, Unadjusted
```{r OCIR retro Model 0a}
ocir_retro_model0a <- lm(
  formula = ocir.diff_score_base_retro ~ 
    Disorder_hierarchical,
  data = dat.retro)

summary(ocir_retro_model0a)
tidy(ocir_retro_model0a)
```

Model 0b: Overlapping disorders, Unadjusted
```{r OCIR retro Model 0b}
ocir_retro_model0b <- lm(
  formula = ocir.diff_score_base_retro ~
    anxiety_disorders +
    depressive_disorders +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder,
  data = dat.retro)

summary(ocir_retro_model0b)
tidy(ocir_retro_model0b)
```

Model 1a: Disorder hierarchical, Adjusted
  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r OCIR retro Model 1a}
ocir_retro_model1a <- lm(
  formula = ocir.diff_score_base_retro ~ 
    Disorder_hierarchical + 
    Gender_collapsed + 
    age_category + 
    Ethnicity_collapsed + 
    time_diff_sign_up_coping,
  data = dat.retro)

summary(ocir_retro_model1a)
tidy(ocir_retro_model1a)
```

Model 1b: Overlapping disorders, Adjusted
  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r OCIR retro Model 1b}
ocir_retro_model1b <- lm(
  formula = ocir.diff_score_base_retro ~
    anxiety_disorders +
    depressive_disorders +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder +
    Gender_collapsed + age_category + Ethnicity_collapsed + time_diff_sign_up_coping,
  data = dat.retro)

summary(ocir_retro_model1b)
tidy(ocir_retro_model1b)
```
